\section{Market Manipulation}
The medium of exchange is a widely accepted instrument or asset that serves as a common intermediary for transactions,
facilitating the exchange of goods and services~\cite{mankiw2014principles}. It functions as a standardized unit of
account, allowing the valuation and comparison of different goods and services. The medium of exchange eliminates the
need for barter and enables efficient value transfer in economic transactions ~\cite{friedman2004money}. Manipulation of
the medium of exchange refers to deliberate actions taken to influence or distort its value, availability, or
circulation in order to gain an unfair advantage or control over economic transactions. This manipulation can occur
through various means and can have significant implications for market participants and overall economic stability.

Additionally, manipulation can occur through market interventions, such as insider trading, price manipulation, or
spreading false information to manipulate the perception of value or demand for certain assets or currencies. These
actions can distort market prices, disrupt fair competition, and create opportunities for manipulation by individuals or
institutions with privileged information or significant market power. One way to study the manipulation of the medium of
exchange is through the lens of economics. In this case, the focus would be on understanding how market forces and
government policies affect the supply and demand for different types of currency and other forms of payment. For
example, a country's central bank may adjust interest rates or change monetary policy in order to influence the value of
its currency relative to others. Similarly, the government may regulate financial markets or institute taxes on certain
transactions in order to discourage their use \cite{domanski2011currency}.

In the following sections, we will delve into the various forms of market manipulation a medium of exchahge can be
target of.

\input{tex/2_definitions_of_terms/2_2_market_manipulation/2_2_1_crypto_market_manipulation.tex}
\input{tex/2_definitions_of_terms/2_2_market_manipulation/2_2_2_what_are_spoofing_and_layering.tex}
\input{tex/2_definitions_of_terms/2_2_market_manipulation/2_2_3_spoofing_and_layering_on_bitcoin_trading.tex}