\subsection{How Does Bitcoin Actually Work?}
Bitcoin's creation was prompted by the need for a secure and decentralized system of transferring value. The solution to
this problem involved an intriguing mathematical puzzle that required the invention of new concepts such as digital signatures
and cryptographic hash functions.

Creating a new cryptocurrency is a complex process that involves several steps, including developing a consensus mechanism,
creating a blockchain, implementing security measures, and ensuring decentralization. To understand how Bitcoin works and
identify potential areas for design improvements, it can be helpful to examine the technical details of its underlying
protocols~\cite{nakamoto2008bitcoin}. Alternative cryptocurrencies have emerged as a result of different design choices
made by their creators, which has led to a diverse ecosystem of digital currencies with varying features and use cases.

While the underlying technology may seem complex to some, it is important to note that using a cryptocurrency does not
require an in-depth understanding of its mechanics~\cite{barski2014bitcoin}. Just like swiping a credit card, users can
take advantage of user-friendly applications that enable seamless sending and receiving of these digital assets.

The concept of cryptocurrency revolves around enabling individuals to conduct transactions without relying on a centralized
entity for trust verification. Typically, when using a credit card to purchase goods or services, one must rely on banks
(or a network of banks) to correctly debit the user's account and credit the recipient's account. The majority of currencies
are issued by governments, which can exercise some level of control over their respective currencies through means such
as adjusting the money supply. As a result, holders of these currencies must place a certain degree of trust in the government
issuing them to manage them effectively.

The concept of Bitcoin was inspired by the desire to overcome the limitations of traditional financial systems. According
to Nakamoto (2008, p.1)~\cite{nakamoto2008bitcoin}:

\begin{displayquote}
    \textit{the root problem with conventional currencies is all the trust that's required to make it work}
\end{displayquote}

To address this issue, Bitcoin was designed as a decentralized digital currency that operates without a central authority
or intermediary. The money supply of Bitcoin is fixed and determined by its underlying algorithm, making it resistant to
inflation and manipulation. In addition, transactions in the Bitcoin network are recorded on a public ledger called the
blockchain, which ensures transparency and accountability. Bitcoin allows for direct peer-to-peer payments without the need
for intermediaries, such as banks or payment processors. This property of Bitcoin eliminates the need for trust in a central
authority and enables participants to transact with each other directly, thereby reducing transaction costs and increasing
efficiency.

The concept of decentralization in trustless payment systems has been subject to debate among readers. However, this discussion
is beyond the scope of our current topic. While personal needs for trustless payments may vary, the question of whether
such a system is technically feasible remains an intriguing one. Cryptography, which originated from encrypting messages,
employs deep mathematical concepts to achieve its objectives. The remarkable effectiveness of cryptographic tools extends
beyond confidential communication into other domains. For instance, the development of a decentralized currency presents
a significant challenge that can be addressed by applying cryptographic techniques~\cite{diffie2022new}.

\input{tex/1_introduction/1_2_bitcoin_a_peer_to_peer_electronic_cash_system/1_2_2_creating_your_own_cryptocurrency.tex}
