\subsection{Spoofing, Layering, and High-Frequency Trading}

Spoofing and layering are not limited to electronic trading but can also occur in manual and non-electronic trading settings.
However, the majority of spoofing cases that have been prosecuted thus far have occurred in the context of automated (algorithmic)
trading, particularly within the realm of high-frequency trading (HFT). It is expected that in the future, spoofing will
predominantly be carried out by traders utilizing algorithms and engaging in HFT practices. The association between spoofing
and HFT is undeniable, as HFT provides a conducive environment for executing spoofing and layering schemes, which can enhance
the financial gains for traders involved. HFT's speed enables traders to minimize the risk of other market participants
trading against their spoof orders by swiftly canceling those orders in response to upward price movements. Given that HFT
has opened avenues for spoofing and layering, it is essential to consider spoofing enforcement within the broader framework
of HFT regulation.

HFT has experienced substantial growth in the past 15 years, reaching its peak in 2009, and continues to account for a
significant portion of trading volume in both U.S. equities and futures markets. Purported advantages of HFT include reduced
short-term market volatility, narrower bid-ask spreads for large-cap stocks, and increased market liquidity and efficiency.
However, these advantages are accompanied by perceived drawbacks such as declines in market integrity, fairness, and the
quality of liquidity. Concerns regarding these disadvantages have prompted the introduction of federal legislation aimed
at regulating HFT, although no such bill has been enacted to date. Additionally, regulatory bodies such as the U.S.
Securities and Exchange Commission (SEC), the U.S. Commodity Futures Trading Commission (CFTC), and exchanges have largely
refrained from implementing specific regulatory measures targeting HFT \cite{chilton2012perspectives}.

Proposed regulations aimed at addressing high-frequency trading (HFT) encompass a range of measures, including: (1) the
implementation of speed bumps to introduce delays in orders or information, thereby reducing the speed advantage enjoyed
by HFT firms over other investors; (2) the requirement for proprietary HFT firms meeting specific criteria to register
with regulatory bodies such as the U.S. Commodity Futures Trading Commission (CFTC), U.S. Securities and Exchange Commission
(SEC), or the Financial Industry Regulatory Authority (FINRA); (3) the introduction of a financial transaction tax
specifically targeting HFT firms; (4) the prohibition of co-location, which involves HFT firms and brokers paying
exchanges to place their servers in the same physical location to minimize latency periods; and (5) the implementation
of order cancellation fees. Although these proposals have faced considerable obstacles in the United States, certain
exchanges have taken steps to introduce speed bumps. It is worth noting that HFT is not limited to the United States,
and other jurisdictions have been more proactive in regulating such trading practices. Notably, the European Union's
MiFid II Directive (effective in 2018) and Market Abuse Regime (effective in 2016) represent the world's most comprehensive
set of rules governing HFT. These regulations cover various aspects, including market access for HFTs, algorithm monitoring,
redefinition of market manipulation in light of HFT, classification of spoofing and layering as forms of market manipulation,
and the exclusion of intent as an element for civil offenses related to spoofing and layering. Arguments advocating for
harmonizing the U.S. approach to HFT with that of the EU hold merit. However, it is important to note that while the United
States has not expressly criminalized spoofing, the United Kingdom has not yet seen criminal prosecutions for spoofing
\cite{angel2020spoofing, chilton2012perspectives, cataldo2019making}.