\subsection{The Illusion of Money}
From Ancient Kings to modern day governments and Central Banks, money has remained an illusion. A mere representation whose value is determined
by the importance people place on it.

The ten thousand Singapore Dollars banknote, while no longer in production, remains the highest denomination in circulation \cite{goodhart1998}.
Despite its intrinsic production cost of less than 20 cents, the value of this paper note is upheld by the illusion perpetuated by the fiat
currency system \cite{gupta2019}. Presently, its monetary equivalence to seven thousand three hundred and forty-five US Dollars enables its
utilization in acquiring substantial assets such as houses, cars, and even valuable commodities like gold.

“Fiat” is the fancy word we use to describe the modern-day illusion. It's a Latin word that translates to “let it be done.” It's a decree by
the government that, in the case of money, determines what its value is and enforces it as legal tender \cite{reinhart2018, friedman2000}.

The elusive nature of money often evades careful consideration, yet akin to historical rulers, contemporary governments possess an understanding
of the influential power of currency and persistently strive for its accumulation, as expounded by Graeber \cite{graeber2011}. Recognizing that
the possession of greater quantities of these paper instruments equates to amplified authority, governments adopt the approach of generating
additional currency ex nihilo, as highlighted by Mankiw \cite{mankiw2014}. For instance, in the scenario where the United States government
necessitates \$340 million dollars to procure an F-22 jet, it possesses the capacity to create the required funds through the act of monetary
printing.

But there is one problem with this: inflation.

The fundamental attribute of money lies in its role as a medium of exchange, conferring value upon it, as emphasized by Mankiw \cite{mankiw2014}.
Consequently, the quantity of money in circulation should align with the aggregate production of goods and services. Should the issuance of
money exceed the availability of goods and services, with all else remaining constant, the resultant effect is an escalation in prices and a
subsequent devaluation of the currency itself. This concern resonates with economists and the general population, including individuals such as
ourselves, as underscored by Blinder \cite{blinder2010}, particularly in the context of the current global reserve currency, the United States
Dollar.

The year 2020 proved to be an exceedingly challenging period for the world at large, as the onset of the pandemic necessitated the temporary
closure of numerous economies, resulting in a considerable reduction in the availability of goods and services and a marked decline in overall
economic output, as outlined in the World Economic Outlook report by the International Monetary Fund \cite{imf2020}. In an effort to avert
economic collapse and the potential disintegration of societal systems, the US government embarked on an unprecedented scale of monetary
expansion, surpassing any previous instances of currency printing in its history \cite{blinder2020}. As in 2021, the current state of affairs
reveals a considerable expansion of the US dollar supply, with approximately 40\% of the existing currency having been printed within the last
18 months \cite{fedmoneysupply}. This substantial increase in money supply in relation to the country's output has raised concerns regarding
the potential for significant price inflation \cite{Blanchard2021}. Observable evidence of this trend is already apparent in the substantial
rise in commodity prices, such as the tripling of lumber prices compared to a year ago. Additionally, discernible price increases can be
observed in everyday experiences, including slight increments in prices at favorite restaurants, such as a modest 20-cent rise in the cost of
guacamole at Chipotle \cite{BLS}. Although the provision of stimulus and unemployment checks by governments to their citizens may initially
appear beneficial, it entails a double-edged sword. While it undoubtedly assists individuals in dire economic circumstances, it also introduces
challenges. Presently, the combined factors of inflationary pressures and economic slowdown have created difficulties for individuals seeking
suitable employment opportunities, not solely due to a lack of willingness, but also because certain job options may be less desirable than
available alternatives \cite{cbo2020, kahn2020}.

An illustrative example can be observed in the United States, where the law does not mandate a minimum wage for individuals working as waiters
or waitresses \cite{dol}. Consequently, some employees in these roles receive meager hourly wages, such as \$2 to \$3, with tips constituting
a substantial portion of their earnings. However, due to the implementation of various restrictions and regulations nationwide, coupled with a
decrease in customer traffic, there has been a reduction in both customer volume and disposable income, thereby leading to a decline in tip
revenue \cite{bls2022}. Inadequate income for employees may result in higher turnover rates as financial needs are not being met. This situation
poses a significant risk to businesses, as the lack of a sufficient workforce can ultimately lead to business closure, setting in motion a
cascading effect \cite{azar2020}. A valid concern arises regarding the motivation to actively seek employment when the potential income from
unemployment and stimulus checks surpasses that from being employed. This circumstance prompts an examination of available options. Notably,
the Federal Reserve of the United States employs a strategic approach to injecting funds into the economy, a process that may not be widely
acknowledged, thus stimulating economic activity without substantial public scrutiny \cite{frb}. Consequently, the relative attractiveness of
alternative income sources may influence individuals' decision-making regarding employment prospects \cite{cbo2021}.

The United States had accumulated a staggering national debt of \$29 trillion prior to 2020, an astounding and challenging figure to comprehend
\cite{usdebt}. This debt is primarily financed through the issuance of bonds and treasury notes, which are essentially contractual instruments
offering repayment of a predetermined principal sum alongside interest \cite{treasurysecurities}. Presently, investing in a 10-year U.S.
Treasury bond would yield a modest return of 1.23\% upon maturity. Therefore, investing \$1,000 today would result in a nominal return of a
mere \$12.30 by 2031. However, this return fails to keep pace with the targeted inflation rate, projected to be around 2\% annually
\cite{frbinflation}. It should be noted that actual inflation rates may surpass the target, although that discussion is beyond the scope of the
current context. Consequently, investing in government notes issued by one's own country, whose currency is utilized in daily transactions,
leads to a gradual erosion of purchasing power over the course of a decade. Irrespective of these concerns, financial institutions, businesses,
and individuals worldwide participate in the acquisition of bonds and treasury notes, thereby providing governments with discretionary funds
for utilization \cite{treasurysecurities}. However, when the government confronts the need to fulfill its debt obligations, the previously
obtained funds have been fully expended. Consequently, the government initiates repurchases of treasuries and bonds, confining such transactions
to prominent financial institutions and remunerating them by means of freshly created money, effectively conjured from nothingness. The Federal
Reserve, for instance, has repurchased over \$1 trillion in bonds since March 2020, with plans to persist in such actions well into the future
\cite{federalreserve}.

By virtue of government injections, banks are empowered to expand their lending activities, thereby increasing interest income and fostering
economic growth \cite{federalreserve}. However, this surge in lending concurrently expands the aggregate money supply, leading to a depreciation
in the value of each individual dollar. The implementation of multi-trillion dollar stimulus payments and infrastructure packages raises questions
regarding the sustainability of such practices. The influx of new money results in a devaluation of existing money, whereby the balance in an
individual's bank account remains unchanged, yet its purchasing power diminishes owing to the influx of newly minted money
\cite{currencydevaluation}. Consequently, the retention of wealth in a fiat currency like the US dollar progressively erodes its value,
ultimately impeding the ability to acquire goods and services despite nominal bank balances.

The reality that money is nothing but an illusion is one that we must all embrace. Because only then will the path to financial freedom become
clearer. Understanding that money does not have any intrinsic value in itself, but instead only inherits the value we give to it.

As the money supply continues to expand, the purchasing power of each individual dollar held in one's possession inevitably erodes, whereas the
dollar-denominated value of global assets tends to appreciate \cite{moneyprinting}. Nevertheless, this perceived growth can be likened to an
optical illusion, employing deceptive mechanisms. Despite the seemingly unrelenting ascent of the stock market, the underlying reality is far
from reassuring. The relentless depreciation of the currency compounds the situation, eroding its value on a daily basis. For example, if the
Dow Jones Industrial Average, which serves as a benchmark for the performance of 30 major US companies, were denominated in terms of gold rather
than USD, it becomes apparent that its value has essentially stagnated since 1997 \cite{stockmarketillusion}.

But what's the end goal of all of this? With fiat and an unlimited supply of money, will the value of each currency just continue to decrease
until the end of time? Will the gap between the rich and the poor continue to grow wider? Or are we going to finally fix a problem as old as
man itself, and stop placing our financial success in the hands of those who are destroying it day by day? Money is corruptible.

Only time will tell, but just to know, there is a way out: \textbf{Bitcoin}.
