\section{Schedule}
\label{sec:schedule}

\begin{tabular}{@{}l@{}p{1cm}@{}p{1cm}@{}p{1cm}@{}p{1cm}@{}p{1cm}@{}p{1cm}@{}p{1cm}@{}}
    \toprule
    &\Heading{2023}& & & & \Heading{2024}\\
    \toprule
    &\Heading{Sep}&\Heading{Oct}&\Heading{Nov}&\Heading{Dec}&\Heading{Jan}&\Heading{Feb}&\Heading{Mar}\\
    \midrule
    Data Collection & \timebar{2} & & & & \\
    Set Up the Model Environment & & \timebar{1} & & &\\
    Fine-Tuning Pre-Trained Models & & \timebar{2} & & &\\
    Result's Discussion & & & & \timebar{2} &\\
    Configure the Training Script & & & & \timebar{2} &\\
    Training the Model & & & & \timebar{3} &\\
    Fine-tuning and Model Optimization & & & & \timebar{3} &\\
    Result's Discussion & & & & \timebar{2} &\\
    Deploy the Trained Model & & & & \timebar{3} &\\
    Thesis Writing & & \timebar{5} \\
    Preparation of Presentation & & & & & & \timebar{2}\\
    \bottomrule
\end{tabular}
\\

We plan to initiate and finish \emph{Data Collection} within two months, starting in October 2023. In this phase, data
from the Mercado Bitcoin public API will be collected to form two datasets: one containing historical data on which we
plan to forecast the Bitcoin price, and a second one containing the actual movement price of Bitcoin. With this, we can
analyze the market for fraud. More about the dataset is in \ref{data:data_collection}.

Next, we plan to set up and configure a development environment to conduct our research. Using the cloud powered by
artificial intelligence pipelines

Fine-tuning is where we will be testing already-trained models by using our dataset and goals. In this phase, we plan to
use models trained for financial tasks such as \textit{BloombergGPT}.

At the end of those phases, we will collect results and debate them, checking if we meet the requirements, e.g.,
detecting whether or not spoofing and layering happened by deliberately creating fraudulent data on the market.

On Configure the Training Script, we plan to develop an autonomous training mechanism with a variety of models and
hyperparameters.

Training the model is where the training script will be applied with a different approach. Using or not labeled data,
e.g., telling which movement on the market should be considered a fraud,

Model optimization is where we will deploy the model and maintain it.

The actual writing of the dissertation thesis will take place alongside all the named phases.